\documentclass{article}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\title{Quiz 2}
\author{Abdallah Tantawy \quad BH23500021 \quad BSCS}





\begin{document}
\maketitle


\section*{Quiz 2 Questions}

\subsection*{Multiple Choice Questions}

\begin{enumerate}[label=\arabic*.]
    \item What are the advantages of e-commerce?
          \begin{enumerate}
              \item Availability, limited customer service, limited product experience
              \item Availability, speed of access, limited product experience
              \item \textbf{Availability, Speed of access, wide availability}
          \end{enumerate}
    \item What is Internet?
        \begin{enumerate}
            \item Data sent over the internet is called a message
            \item \textbf{A worldwide computer network that transmits a variety of data and media across interconnected devices.}
            \item Specifies how computers should send information to other computers by sending data with an attached numerical address (IP Address)
            \item Rules that govern how information is sent from one computer to another computer over an internet connection
        \end{enumerate}
    \item B2B is type of e-commerce that refers to transactions that occur as:
        \begin{enumerate}
            \item \textbf{Business-to-business}
            \item Buyer-to-business
            \item Business-to-consumer
            \item Business-to-buyer
        \end{enumerate}
    \item How many types of Internet Protocol are there?
        \begin{enumerate}
            \item 1
            \item \textbf{2}
            \item 3
            \item 4
        \end{enumerate}
    \item Which of the following is an example of a URL?
        \begin{enumerate}
            \item \textbf{www.google.com}
            \item Business-to-buyer
            \item Facebook
            \item Abdallah@Tantawy.com
        \end{enumerate}
    \item Transport Control Protocol (TCP)
        \begin{enumerate}
            \item \textbf{Works with IP to ensure transfer of data is dependable and reliable}
            \item Before messages get sent, they’re broken up into tiny parts called packets Language used for internet communication.
            \item Secure version of HTTP, all communications between your browser and website are encrypted.
            \item Assigned to a device on a closed network such as a home or business network that’s not accessible over the internet
        \end{enumerate}
    
    \item E-commerce is defined as the online exchange of ... between firms and also between firms and their customers.
        \begin{enumerate}
            \item \textbf{Goods, services, money}
            \item Goods
            \item Services
            \item Money
        \end{enumerate}
    
    \item ISP stands for:
        \begin{enumerate}
            \item \textbf{Internet Service Provider}
            \item Internet Protocol
            \item Internet of Things
            \item Internet Protocol Address
        \end{enumerate}
    
    \item It's a language used for internet communication.
        \begin{enumerate}
            \item \textbf{Hypertext Transfer Protocol (HTTP)}
            \item Internet Protocol (TCP)
            \item Internet Protocol Address (HTTPS)
            \item Hypertext Markup Language (HTML)
        \end{enumerate}
    \item Issues with the Internet and the web.
        \begin{enumerate}
            \item Communication, Information sharing, Online addiction and Disinformation.
            \item Online addiction and Disinformation,Online shopping and Entertainment.
            \item Communication ,Information sharing , Online shopping and Entertainment.
            \item \textbf{Privacy and security, Cyberbullying ,Online addiction and Disinformation.}
        \end{enumerate}
    
    \item How does the internet work?
        \begin{enumerate}
            \item It works by using a packet routing network that follows Transport Control Protocol (TCP) ONLY
            \item It works by using a packet routing network that follows Internet Protocol (IP) ONLY.
            \item Rules that govern how information is sent from one computer to another computer over an internet connection
            \item \textbf{It works by using a packet routing network that follows Internet Protocol (IP) and Transport Control Protocol (TCP).}
        \end{enumerate}

    \item Indirect access is
        \begin{enumerate}
            \item \textbf{most common method used in home and office networks.}
            \item most common method used when travelling.
        \end{enumerate}
    
    
    


\end{enumerate}
\subsection*{True or False Questions}

\begin{enumerate}[label=\arabic*.]
    \item Private IP addresses are one type of Internet Protocol (IP)
          \begin{enumerate}
              \item \textbf{True}
              \item False
          \end{enumerate}
    \item A public IP Address is Accessible over the internet.
          \begin{enumerate}
              \item \textbf{True}
              \item False
          \end{enumerate}
    \item Static websites are prebuilt source code files built using simple languages such as HTML, CSS, or JavaScript.
            \begin{enumerate}
                \item \textbf{True}
                \item False
            \end{enumerate}
    \item Before messages get sent, they're broken up into tiny parts called packets.
          \begin{enumerate}
              \item \textbf{True}
              \item False
          \end{enumerate}
    \item Data sent over the internet is called a message.
          \begin{enumerate}
              \item \textbf{True}
              \item False
          \end{enumerate}
    \item Internet Protocol is a company that provides access to the internet to both personal and business customers.
          \begin{enumerate}
              \item True
              \item \textbf{False}
          \end{enumerate}
    \item Static websites are fast because it interact with databases.
          \begin{enumerate}
              \item True
              \item \textbf{False}
          \end{enumerate}
    \item Private IP Addresses are assigned to devices on a closed network such as a home or business network that's not accessible over the internet.
          \begin{enumerate}
              \item \textbf{True}
              \item False
          \end{enumerate}
    \item Public IP addresses are one type of Internet Protocol (IP)
          \begin{enumerate}
              \item \textbf{True}
              \item False
          \end{enumerate}
    \item PAN allows for easy communication between personal devices in close proximity.
            \begin{enumerate}
                \item \textbf{True}
                \item False
            \end{enumerate}
    \item Dynamic websites are web pages returned by the server that are processed during runtime means they are not prebuilt web pages.
            \begin{enumerate}
                \item \textbf{True}
                \item False
            \end{enumerate}
    \item PAN is the most basic type of computer network
            \begin{enumerate}
                \item \textbf{True}
                \item False
            \end{enumerate}
    \item Internet of Things (IoT) is a network of physical devices that can transfer data to one another without human intervention.
            \begin{enumerate}
                \item \textbf{True}
                \item False
            \end{enumerate}
    \item Advantages of cloud storage are (Total cost of ownership, compliance and latency)
            \begin{enumerate}
                \item True
                \item \textbf{False}
            \end{enumerate}
    \item PAN May have limited security compared to LAN\\
    LAN Can be expensive to set up and maintain\\
    MAN May not be suitable for large-scale data transfer\\
    WAN may not experience interference from other wireless devices.
            \begin{enumerate}
                \item True
                \item \textbf{False}
            \end{enumerate}
    \item Internet Protocol (IP) are rules that govern how information is sent from one computer to another computer over an internet connection.
            \begin{enumerate}
                \item \textbf{True}
                \item False
            \end{enumerate}

     
    

\end{enumerate}

\end{document}
