\documentclass{exam}

\begin{document}

\begin{questions}

\printanswers
\question Which of the following is NOT a learning and support tool for application software?
\begin{checkboxes}
\choice a. Online tutorial
\choice c. User guide
\CorrectChoice b. Software update
\choice d. Online forum or community
\end{checkboxes}

\question What is a man-in-the-middle attack?
\begin{checkboxes}
\choice a. An attack that redirects users to malicious websites.
\choice c. An attack that overwhelms computer systems or networks with traffic, making them unavailable to users.An attack that attempts to break encryption.
\CorrectChoice b. An attack that intercepts communications between two parties and impersonates one of the parties.
\choice d. An attack that overwhelms computer systems or networks with traffic, making them unavailable to users.
\end{checkboxes}

\question 1-You should only install software from trusted sources.
\begin{checkboxes}
\CorrectChoice True
\choice False
\end{checkboxes}

\question What is malware?
\begin{checkboxes}
\choice a. Attacks that attempt to make computer systems or networks unavailable to users.
\choice c. Emails or websites that try to trick users into revealing personal information.
\choice b. Unauthorized access to computer systems or networks.
\CorrectChoice d. Malicious software, such as viruses, worms, and Trojan horses.
\end{checkboxes}

\question Anti-static wristbands are required when troubleshooting hardware problems.
\begin{checkboxes}
\choice True
\CorrectChoice False
\end{checkboxes}

\question What is a DNS poisoning attack?
\begin{checkboxes}
\choice a. An attack that overwhelms computer systems or networks with traffic, making them unavailable to users.
\choice c. An attack that attempts to break encryption.
\CorrectChoice b. An attack that redirects users to malicious websites.
\choice d. An attack that intercepts communications between two parties and impersonates one of the parties.
\end{checkboxes}

\question What is the difference between a communication network and a computer network?
\begin{checkboxes}
\choice a. A communication network is used to transmit data over long distances, while a computer network is used to connect devices within a small area.
\choice c. There is no difference between a communication network and a computer network.
\choice b. A communication network is used to transmit data over a variety of media, such as copper wires, fiber optic cables, and radio waves, while a computer network is typically used to transmit data over copper wires.
\CorrectChoice d. A communication network is used to transmit data between two or more devices, while a computer network is used to connect computers together.
\end{checkboxes}

\question What is the purpose of gathering information during the troubleshooting process?
\begin{checkboxes}
\choice a. To verify that the solution has resolved the problem
\choice c. To identify the cause of the problem
\CorrectChoice b. All of the above
\choice d. To develop a solution to the problem
\end{checkboxes}

\question What is the first step in the troubleshooting methodology?
\begin{checkboxes}
\choice a. All of the above
\choice c. To verify that the solution has resolved the problem
\choice b. To develop a solution to the problem
\CorrectChoice d. Identify the problem
\end{checkboxes}

\question What is phishing?
\begin{checkboxes}
\choice a. Malicious software, such as viruses, worms, and Trojan horses.
\CorrectChoice c. Emails or websites that try to trick users into revealing personal information.
\choice b. Attacks that attempt to make computer systems or networks unavailable to users.
\choice d. Unauthorized access to computer systems or networks.
\end{checkboxes}

\question What is the best way to troubleshoot a problem that you can't figure out on your own?
\begin{checkboxes}
\choice a. Ask a friend or colleague for help
\choice c. Contact the manufacturer of your hardware or software
\choice b. Search the internet for help
\CorrectChoice d. All of the above
\end{checkboxes}

\question Computer security is only important for businesses.
\begin{checkboxes}
\choice True
\CorrectChoice False
\end{checkboxes}

\question Which of the following is an example of application software for communication?
\begin{checkboxes}
\choice a. Spreadsheet
\choice c. All of the above
\choice b. Word processor
\CorrectChoice d. Email client
\end{checkboxes}

\question 1-A communication network is a system of interconnected devices that allows users to communicate with each other.
\begin{checkboxes}
\CorrectChoice True
\choice False
\end{checkboxes}

\question What is the best way to troubleshoot overheating problems?
\begin{checkboxes}
\choice a. Use a cooling pad or fan to keep your laptop cool
\CorrectChoice c. All of the above
\choice b. Clean the dust out of your computer case and fans
\choice d. Make sure that your computer is properly ventilated
\end{checkboxes}

\question Antivirus software is enough to protect your computer from all security threats.
\begin{checkboxes}
\choice True
\CorrectChoice False
\end{checkboxes}

\question You should never use public Wi-Fi networks EVEN if you are using a VPN.
\begin{checkboxes}
\choice True
\CorrectChoice False
\end{checkboxes}

\question What are the benefits of using a cloud-based video conferencing system for business communication?
\begin{checkboxes}
\choice a. It is secure, reliable, and offers high-quality video and audio.
\CorrectChoice c. All of the above.
\choice b. It is compatible with all devices and operating systems.
\choice d. It is easy to use, affordable, scalable, and accessible from anywhere.
\end{checkboxes}

\question What is VoIP?
\begin{checkboxes}
\choice a. All of the above
\choice c. Virtual Private Network
\CorrectChoice b. Voice over IP
\choice d. Video over IP
\end{checkboxes}

\question What is the best way to troubleshoot dropped packets?
\begin{checkboxes}
\choice a. Update the firmware on your network devices
\CorrectChoice c. All of the above
\choice b. Check the network cables for damage
\choice d. Reduce the amount of traffic on your network
\end{checkboxes}

\question What is the best way to prevent hardware and network problems from occurring?
\begin{checkboxes}
\choice a. Use a firewall and antivirus software
\choice c. Regularly back up your data
\CorrectChoice b. All of the above
\choice d. Keep your software up to date
\end{checkboxes}

\question What is the best way to test a hypothesis during the troubleshooting process?
\begin{checkboxes}
\choice a. Perform tests that are relevant to the hypothesis
\choice c. Use multiple tests to confirm or disprove the hypothesis
\CorrectChoice b. All of the above
\choice d. Document the results of the tests
\end{checkboxes}

\question What is the most common cause of slow internet speeds?
\begin{checkboxes}
\choice a. High network traffic
\choice c. Faulty network hardware
\choice b. Weak Wi-Fi signal
\CorrectChoice d. All of the above
\end{checkboxes}

\question What is the best way to troubleshoot lost connections?
\begin{checkboxes}
\choice a. Ping devices on your network to test connectivity
\CorrectChoice c. All of the above
\choice b. Restart your network router and modem
\choice d. Check the physical connections between your devices and your network
\end{checkboxes}

\question It is okay to reuse passwords for different accounts.
\begin{checkboxes}
\choice True
\CorrectChoice False
\end{checkboxes}

\end{questions}

\end{document}